\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[]{amsthm} %lets us use \begin{proof}
\usepackage[]{amssymb} %gives us the character \varnothing
\usepackage{amsmath}

\topmargin=-1in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6in
\textheight=9.0in

\title{ZK Bootcamp: Homework 1}
\author{Kuriakin Zeng}
\date\today
%This information doesn't actually show up on your document unless you use the maketitle command below

\begin{document}
\maketitle %This command prints the title based on information entered above

\section*{Math Introduction}

\subsection*{Problem 1}
Working with the following set of Integers $S = \{0,1,2,3,4,5,6\}$, what is:
\begin{itemize}
\item $4+4 \equiv 1 \pmod 7$
\item $3 \cdot 5 \equiv 1 \pmod 7$
\item By Fermat's Little Theorem, $3^{-1} \equiv 3^{7-2} \pmod 7 \equiv 5 \pmod 7$
%\item $3^{-1} \equiv 5$ 
\end{itemize}
\subsection*{Problem 2}
$S = \{0, 1, 2, 3, 4, 5, 6\}$ and operation $+$ is a group.
\begin{proof}
For any $a,b,c \in S$
\begin{itemize}
\item Closure. It's easy to see that $a+b \pmod 7 \in S$
\item Associativity. $S$ is a subset of integers, thus $(a+b)+c = a+(b+c)$
\item Identity. The identity element is 0 since $a + 0 = a$
\item Inverse element. It's easy to see that, by FLT, $-a \equiv 5a \pmod 7$ and $-a + 5a = 4a \pmod 7 \in S$
\end{itemize}
\end{proof}
\subsection*{Problem 3}
$-13 \pmod 5 \equiv 2 \pmod 5$

\section*{Use cases of zkp}
\begin{itemize}
\item Authenticate users without exchanging secret information such as passwords
\item Allow one to prove that they satisfy a requirement without revealing the data itself. For example, proving that one's income is in admissable range for a loan
\item Allow voters to vote anonymously without compromising the legitimacy of the votes
\end{itemize}
However, zkp has a few challenges.
\begin{itemize}
\item As demonstrated by the ball-picking example, the probability of the prover lying decreases with each iteration but ZKP's don't guarantee 100\% that the prover isn't lying
\item zkps require many interactions between the verifier and the prover in interactive ZKP's or require a great deal of computations in non-interactive ZKP's. They may not be suitable for slow or mobile devices.
\end{itemize}

\clearpage %Gives us a page break before the next section. Optional.

\end{document}